The purpose of this ungraded assignment is to give you the opportunity to express your interests and enable the instructors to “get to know” you better.  If you need more space, attach an additional sheet of paper.
You will have considerable freedom to select topics for study in this course, and the dialogue that we are beginning here will assist me in guiding your choices. Let’s continue to communicate throughout the semester.  


**** Put your name on the questionnaire
**** What do you plan to do when graduating? (chem Eng job descriptions)
**** Have laptop or tablet?
**** Have internet access e.g. via phone or portable computer?
**** Started your own company? Ever thought about it?
**** Job lined up?
**** Do you have a laptop, tablet computer that you can bring to class
**** Do you have a cell phone with internet (data) access?
**** What do you plan to do when you graduate?
**** What did you do last summer?
**** Top three group members or checkbox: no preference, please assign me randomly
**** My grade in 3G:
**** Other courses I am taking this semester
* Not asked: Have you filed a Canadian tax return for 2011?
* Not asked: What's your cell phone signal like in the class?



1.  Briefly describe your dream first job or topic for graduate studies and research.
2.  What is your long-term career goal?
3.  What did you do during the summer (or during your internship)?


1. Are course evaluations from previous years available (not the instructor part, just the course content part)
2. Typical load outside teaching time: office hours, walk-in student questions
3. Use of extra-credit / not-for-credit assignments
4. Audio-visual equipment available?
5. Class duration: 3 hours.  Can it be changed.
6. Course materials copyright:

Issue is that generally, the university owns the copyright to materials produced by non-faculty members. 

But there is an exception when the materials are created outside their job description.

The issue is that my job description doesn't explicitly state what is required/not required.  

Since the university's policy does allow for exceptions, would it be possible to have a letter from the departmental head, similar to my offer letter: 

	"You will retain copyright of course materials you develop for McMaster
	 University for the ChE4C3/ChE6C3 course"

Since the university's usual policy is also that materials created by faculty are not available for re-use by other faculty: I'm happy to make all my materials available under the Creative Commons Share Alike license.  This allows the university non-exclusive, perpetual use of the materials, while still allowing myself to own the copyright and reuse the course materials.
